Typed Functional Genetic Programming

### 2013-08-01 tex/thesis.tex
čtvrtek 9:34

\begin{todo}
& definovat \textbf{CR} a říct o tom lemátku, že má CR redukce má unikátní nf.
&& V \cite{barendregt84} (ta nová kniha s žlutejma deskama) je ukázano že je eta CR (Church Rosserovská)
& zmínit Theorem 2B.4 z \cite{barendregt10}
\end{todo}

@@

\begin{todo}
   & říct že se vždycky zastavěj (strong normalization)
     && a jaký to má výhody pro nás v GP (duležitý),
     && potřebný definice pro to uvést v \lterms sekci
     && musí se říct co je strongly normalizing, 
        tzn simpli typed $lambda$-kalkulus termy a $\beta$-redukce /
        $\beta\eta$-redukce
%     && řekl bych že eta redukce je SN vždycky (tzn i untyped lk)
%        pač plati (CR+terminující pak SN) a je CR vzhledem k barendrecht-stará-žlutá
%        a terminující je rpotože zmenšuje term s nemuže zmenšovat donekonečna    
\end{todo}

@@

\begin{enumerate}
 \item Every application of \ered shortens the term.
       Since every term has finite size, this process must 
       end at some point. Thus every \lterm has \enf.
 \item Since \ered is \textbf{CR}, \enf is unique (see \ref{todo}). 
\end{enumerate}

@@

Another nice property of \sexprTree{}s with no lambdas 
is that they are the same representation as S-expressions
used by standard GP.

@@

@@

@@

\appendix
\chapter{First Appendix}

abc

>>>>

@@

Nice thing about \textit{simply typed lambda calculus} is that
program $M$ such that \GMS always terminates 
(provided that implementations of function symbols in $\Gamma$ 
also always terminate). This fact is particularly handy for
GP --- we can evaluate bred programs without worrying about hanging
in the infinite loop forever.

%\begin{todo}
%   & říct že se vždycky zastavěj (strong normalization)
%     && a jaký to má výhody pro nás v GP (duležitý),
%     && potřebný definice pro to uvést v \lterms sekci
%     && musí se říct co je strongly normalizing, 
%        tzn simpli typed $lambda$-kalkulus termy a $\beta$-redukce /
%        $\beta\eta$-redukce
%%     && řekl bych že eta redukce je SN vždycky (tzn i untyped lk)
%%        pač plati (CR+terminující pak SN) a je CR vzhledem k barendrecht-stará-žlutá
%%        a terminující je rpotože zmenšuje term s nemuže zmenšovat donekonečna    
%\end{todo}

@@

\begin{enumerate}
 \item Every application of \ered shortens the term.
       Since every term has finite size, this process must 
       end at some point. Thus every \lterm has \enf.
 \item Since \ered is \textit{Church–Rosser}, \enf is unique (see \cite{barendregt84}). 
\end{enumerate}

@@

Another nice property of \sexprTree{}s with no lambdas 
is that they are the same representation as S-expressions
used by standard GP.\\

Again, similarly as for standard version, 
a maximum permissible depth $D_{created}$ 
for offspring individuals is defined (e.g. $D_{created} = 17$).
If one of the offspring has greater depth than this limit, then 
this offspring is replaced by the first parent in the result of 
the crossover operator. If both offspring exceeds this limit, than 
both are replaced by both parents.

For \atTree the $D_{created}$ must be larger since
\atTree (without lambdas) is a binary tree. This 
enlargement is approximately proportionate to average number of 
function arguments. We use generous $D_{created} = 17\times3$.

@@

%Performance curves are following.

@@

\includegraphics[scale=0.5]{reports/Ant/p.png}

@@

\appendix
\chapter{Enclosed CD}

The enclosed CD contains implementation source codes,
installation instructions and some other material, 
all described in a greater detail in the \texttt{readme.txt}
file.
